Scaling up the hyperparameter grid for Naomi

### 2023-03-22 src/dev_scale-grid/scale-grid.Rmd
More testing of PCA approach

@@

@@

gaussian_2d <- pca_rescale(m = mu, C = cov, s = 1, k = 5)

plot +
  geom_point(
    data = data.frame(mvQuad::getNodes(gaussian_2d)) %>%
      mutate(weight = mvQuad::getWeights(gaussian_2d)),
    aes(x = X1, y = X2, size = weight),
    col = multi.utils::cbpalette()[2],
    inherit.aes = FALSE
  ) +
  scale_size_continuous(range = c(1, 2))
```

Test how this PCA grid works for some simple integrals.
We will use Alex's [unit tests](https://github.com/awstringer1/aghq/blob/master/tests/testthat/setup-01-optimization.R) from the `aghq` package.

@@

@@

@@

plot_points <- function(gg) {
  gg$nodes %>%
    as.data.frame() %>%
    mutate(weights = gg$weights) %>%
    ggplot() +
    geom_point(
      aes(x = V1, y = V2, size = weights),
      alpha = 0.8,
      col = multi.utils::cbpalette()[2],
      inherit.aes = FALSE
    ) +
    scale_size_continuous(range = c(1, 2)) +
    labs(x = "", y = "", size = "Weight") +
    theme_minimal()
}

{plot_points(pca_grid_bfgs_2d_1) + plot_points(pca_grid_bfgs_2d_3)} / {plot_points(pca_grid_bfgs_2d_5) + plot_points(pca_grid_bfgs_2d_7)}

>>>>

#### Gaussian

@@

obj_list <- list(
  fn = obj,
  gr = function(theta) numDeriv::grad(obj, theta),
  he = function(theta) numDeriv::hessian(obj, theta)
)

@@

pca_grid <- pca_rescale(m = mu, C = cov, s = 1, k = 5)

plot +
  geom_point(
    data = data.frame(mvQuad::getNodes(gaussian_2d)) %>%
      mutate(weight = mvQuad::getWeights(gaussian_2d)),
    aes(x = X1, y = X2, size = weight),
    col = multi.utils::cbpalette()[2],
    inherit.aes = FALSE
  ) +
  scale_size_continuous(range = c(1, 2))

opt_bfgs <- aghq::optimize_theta(obj_list, mu, control = default_control(method = "BFGS"))
norm_bfgs_1 <- aghq::normalize_logpost(opt_bfgs, 1, 1)
exp(norm_bfgs_1$lognormconst)
```

#### Other 2D function

More complicated two dimensional function from Alex's [unit tests](https://github.com/awstringer1/aghq/blob/master/tests/testthat/setup-01-optimization.R) from the `aghq` package.

@@

grid <- expand.grid(
  theta1 = seq(0, 4, length.out = 400),
  theta2 = seq(0, 4, length.out = 400)
)

ground_truth <- data.frame(grid) %>%
  rowwise() %>%
  mutate(pdf = exp(objfunc2d(x = c(theta1, theta2))))

plot <- ggplot(ground_truth, aes(x = theta1, y = theta2, z = pdf)) +
  geom_contour(col = multi.utils::cbpalette()[1]) +
  coord_fixed(xlim = c(0.8, 2), ylim = c(0.8, 2), ratio = 1) +
  labs(x = "", y = "") +
  theme_minimal()

@@

grid_bfgs_2d_1 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 1)
# Error in rescale.NIGrid(grid_bfgs_2d_3, m = opt_bfgs_2d$mode, C = solve(opt_bfgs_2d$hessian)) :
# (in rescale) no appropriate covariance matrix C
# mvQuad::rescale(grid_bfgs_2d_1, m = opt_bfgs_2d$mode, C = solve(opt_bfgs_2d$hessian))

grid_bfgs_2d_3 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 3)
# Error in rescale.NIGrid(grid_bfgs_2d_3, m = opt_bfgs_2d$mode, C = solve(opt_bfgs_2d$hessian)) :
# (in rescale) no appropriate covariance matrix C
# mvQuad::rescale(grid_bfgs_2d_3, m = opt_bfgs_2d$mode, C = solve(opt_bfgs_2d$hessian))

grid_bfgs_2d_5 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 5)
# Error in rescale.NIGrid(grid_bfgs_2d_3, m = opt_bfgs_2d$mode, C = solve(opt_bfgs_2d$hessian)) :
# (in rescale) no appropriate covariance matrix C
# mvQuad::rescale(grid_bfgs_2d_5, m = opt_bfgs_2d$mode, C = solve(opt_bfgs_2d$hessian))

grid_bfgs_2d_7 <- mvQuad::createNIGrid(dim = 2, type = "GHe", level = 7)
# Error in rescale.NIGrid(grid_bfgs_2d_3, m = opt_bfgs_2d$mode, C = solve(opt_bfgs_2d$hessian)) :
# (in rescale) no appropriate covariance matrix C
# mvQuad::rescale(grid_bfgs_2d_7, m = opt_bfgs_2d$mode, C = solve(opt_bfgs_2d$hessian))

@@

plot_points <- function(gg) {
  plot +
    geom_point(
      data = mvQuad::getNodes(gg) %>%
        as.data.frame() %>%
        mutate(weights = mvQuad::getWeights(gg)),
      aes(x = V1, y = V2, size = weights),
      alpha = 0.8,
      col = multi.utils::cbpalette()[2],
      inherit.aes = FALSE
    ) +
    scale_size_continuous(range = c(1, 2)) +
    labs(x = "", y = "", size = "Weight") +
    theme_minimal()
}

#' AGHQ
{plot_points(grid_bfgs_2d_1) + plot_points(grid_bfgs_2d_3)} / {plot_points(grid_bfgs_2d_5) + plot_points(grid_bfgs_2d_7)}

#' PCA-AGHQ
{plot_points(pca_grid_bfgs_2d_1) + plot_points(pca_grid_bfgs_2d_3)} / {plot_points(pca_grid_bfgs_2d_5) + plot_points(pca_grid_bfgs_2d_7)}
